%! TEX root = ../main.tex

\chapter{The Pierre Auger Observatory}
\label{chap:pierre-auger-observatory}

The \PAO is the (by area) largest scientific experiment in the world. It 
consists of an array of 1660 \WCDs, which form the \SD, and 27 fluorescence 
telescopes, that make up the \FD.

With a region spanning roughly \SI{3000}{\kilo\meter\squared} it offers a unique
possibility to observe \UHECRs at the tail-end of the \CR energy spectrum. 

We begin this chapter in \cref{sec:science-case} by stating the design 
intentions and formulating open questions that the \PAO aims to answer. Design
details for the \FD and for the \SD are given in \cref{sec:fd} and \cref{sec:sd} 
respectively. After a discussion on the local \DAQ process and the centralized 
event detection in \cref{sec:cdas}, we finish by detailing the procedure of the
event reconstruction and higher level analysis in \cref{sec:rec}.

\section{Science Goal and Open Questions}
\label{sec:science-case}

The flux of cosmic rays with energies exceeding the ankle, $\SI{5e18}{\eV}$, is 
very low, and measures approximately 1 event per \SI{}{\km\squared\sr\year}
\cite{Fenu2023}. It is evident that one needs a large detector and a lot of time
in order to make statistically relevant statements about the physics of \UHECRs.
Altough only one of the initially planned two data taking sites 
\cite[for white paper see][]{Zavrtanik2000} has been constructed, the Pierre
Auger observatory is a world-leading experiment in terms of measured exposure.

Many insights, such as the existence of the \CR dipole discussed in ?????
\todo{write this}, 
have been gathered by the Auger collaboration as a consequence.
Still, a plethora of mysteries remain. It follows a list of, in no particular
order, important missing links of information that motivate not least this
thesis, but the continued effort of scientists around the world.

\subsection{Mass Composition}
\subsection{Muon Deficit}
\subsection{Exotic Events}

\section{The Fluoresence Detector}
\label{sec:fd}



\section{The Surface Detector}
\label{sec:sd}



\section{Central Data Acquisition System}
\label{sec:cdas}



\section{\Offline and Event Reconstruction}
\label{sec:rec}

